The Practical Application of MST

### 2021-02-21 article.Rmd
Introduce the IIF

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="True Score")
```
This is already showing us something a little weird. Our D (very easy) module is actually more difficult than our F (moderately hard) module. And the E (moderately easy) module is more difficult at the top end of the scale that the G (very hard) module.

>>>>

ggplot(plotData, aes(x=theta, y=trueScore)) + 
  geom_line(aes(colour=module)) +
  labs(title="Module Characteristic Curve", x="θ", y="True Score")
```
This is already showing us something a little weird. Our D (very easy) module is actually a little bit more difficult than our F (moderately hard) module at the top end of the scale. And the E (moderately easy) module is more difficult than the G (very hard) module. All of the modules are quite similar in terms of difficulty (the MCCs are quite close to each other), and moreover the lines are quite flat - there is little discrimination between them. We'll see how this can be expressed more obivously in the next section.

### Item Information Functions (IIFs)
